Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction

### 2019-03-15 Manuscript_draft/Text.Rmd
creating two separated rmd with figures and text I think is the best

---
title: Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction
author:
- name: Jose B. Lanuza
  affilnum: 1
  email: barragansljose@gmail.com

- name: Ignasi Bartomeus
  affilnum: 2

- name: Tia-Lynn Ashman  
  affilnum: 3

- name: Romina Rader
  affilnum: 1

affiliation:
- affil: University of New England (Australia)
  affilnum: 1
- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
  affilnum: 2
- affil: Department of Biological Sciences, University of Pittsburgh 4249 Fifth Avenue, Pittsburgh, Pennsylvania 15260-3929 USA
  affilnum: 3
output:
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    includes:
      in_header: header.tex
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
  word_document: null
  html_document: null
capsize: normalsize
classoption: a4paper
csl: ecology.csl
documentclass: article
fontsize: 11pt
header-includes: \usepackage{float}
footerdate: yes
geometry: margin=1in
linenumbers: yes
bibliography:
- references.bib
- knitcitations.bib
spacing: doublespacing
abstract: no
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'h')
```

@@

```{r knitcitations, echo=FALSE, cache = FALSE}
library(knitcitations)
cleanbib()   
cite_options(citation_format = "pandoc")
```

\singlespace

\vspace{2mm}\hrule

Pollinator sharing can have negative consequences for plant fitness with the arrival of foreign pollen. However, the mechanisms underlying the variation in outcomes as a result of pollen contribution by different plant species are not yet well understood. We conducted a glasshouse experiment to understand how plant traits and phylogenetic relatedness mediate the impacts of 15 heterospecific pollen transfer. We conducted 1800 reciprocal crosses by experimentally transferring pollen (50%  and 100% foreign pollen ratio) between 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae. Seed set was used as proxy of plant fitness. In the treatments of 100% foreign pollen, we found reduced seed set in X% of the treatments. In the treatments of 50% foreign pollen, we found reduced seed set in 65% of the treatments. Moreover, the reduction in seed set was dependent on the reproductive traits of the pollen recipient, but not the pollen donor or relatedness. Our results show that certain traits of recipient plants, particularly compatibility system, are critical in understanding the costs of heterospecific pollen.

\vspace{3mm}\hrule

*Keywords*: heterospecific pollen, plant reproduction, fitness, interspecific competition, phylogenetic distance.

\doublespace

\bleft

@@

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%', fig.cap="Phylogenetic tree of the ten species used in the experiment from three different families from top to bottom: Brassicaceae, Convolvulaceae and Solanaceae"}
knitr::include_graphics('images/phylo_image.png')
```

**Table 1** Species list with family and genus.
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
Family <- c(rep("Brassicaceae",4), rep("Convolvulaceae", 2), rep("Solanaceae",4))

Genus <- c("Brassica", "Brassica", "Eruca", "Sinapis", "Ipomoea", "Ipomoea", "Capsicum", "Petunia", "Solanum", "Solanum")

Species <- c("Brassica rapa", "Brassica oleracea", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")

table<- data.frame(Family, Genus, Species)
kable(table, format="markdown")
```

@@

\newpage
```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7, fig.cap="Barplot with the different treatments that provide information of the reproductive biology of the ten species. The y axis is the proportion of ovules converted to seed in percentage. The different treatments (N=10) which are presented in the legend are, hand cross-pollination, hand self-pollination, natural selfing and apomixis. More information about these treatments can be found in Methods and Appendices."}
load("r_biology.RData")
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)
ggplot(bio,aes(x=Species,y=value,fill=variable))+
  geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology test")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, face= "italic",family = ""), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
  scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6,fig.cap="The impact of foreign pollen on recipient plant species. Effect sizes (with 95%confidence intervals) of 9 different donor species of heterospecific pollen upon all recipients."}

library(effsize)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)

load("effect_size_species/effect_size_total.RData")

 ggplot(all, aes(Family,Cohen_d,colour=Family_1), size=10) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = "italic"))+ geom_point( aes(colour=Family_1),size=2) +
  geom_errorbar(aes(x = Family, ymin = Lower, 
ymax = Upper,colour=Family_1), width = 0.2, size=0.8, alpha=0.5)+
  scale_color_manual(name  ="Family",values=c( "#0072B2", "#009E73", "#D55E00"), labels=c("Solanaceae", "Convolvulaceae","Brassicaceae"))+
  scale_fill_manual(name  ="Family",values=c( "#0072B2", "#009E73", "#D55E00"), labels=c("Solanaceae", "Convolvulaceae","Brassicaceae"))+
  xlab("") + ylab("Hedges' g") + rotate()+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+scale_alpha(guide = 'none')
```

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,fig.margin = TRUE,cache=FALSE,fig.height=9,fig.width=7,fig.cap="The response of heterospecific pollen upon 10 recipient plant species.  Each panel represents one recipient plant species crossed with 50% mixes of the other 9 species."}

library(effsize)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)

load("effect_size_species/all_effect_size.RData")

#BROL
load("effect_size_species/brol_effect_size.RData")
p1<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title=element_text(size=10),title = element_text(vjust=2),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0,0.3,0,1), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,aes(color=factor(Species_1))) +geom_errorbar(alpha=c(0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5),size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",3),"#E69F00"))+
  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle(substitute(paste("A)",italic(' B. oleracea'))))

#BRRA
load("effect_size_species/brra_effect_size.RData")
pp2<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",2),"#E69F00","#0072B2"))+
  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle(substitute(paste("B)",italic(' B. rapa'))))

#ERSA
load("effect_size_species/ersa_effect_size.RData")
p3<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",1),"#E69F00", rep("#0072B2",3)))+
  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0.3,0,1), "cm"),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'italic', 'italic', 'italic')))+ggtitle(substitute(paste("C)",italic(' E. sativa'))))

#SIAL
load("effect_size_species/sial_effect_size.RData")
p4<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2),"#E69F00", rep("#0072B2",3)))+
  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("D)",italic(' S. alba'))))

#IPAQ
load("effect_size_species/ipaq_effect_size.RData")
p5<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0,0.3,0,1), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",1),"#E69F00", rep("#0072B2",4)))+
  scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("E)",italic(' I. aquatica'))))

#IPPU
load("effect_size_species/ippu_effect_size.RData")
p6<- ggplot(ippu_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+
  theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4),"#E69F00", rep("#009E73",1), rep("#0072B2",4)))+
  scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("F)",italic(' I. purpurea'))))

#CAAN
load("effect_size_species/caan_effect_size.RData")
p7<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0.3,0,1), "cm"),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",3),"#E69F00", rep("#009E73",2), rep("#0072B2",4)))+
  scale_fill_manual("Species_1",values=c(rep("#D55E00",3),"#E69F00", rep("#009E73",2), rep("#0072B2",4)))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("G)",italic(' C. annuum'))))

#PEIN
load("effect_size_species/pein_effect_size.RData")
p8<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),axis.text.y = element_blank(),plot.margin = unit(c(0,0,0,0), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",2),"#E69F00","#D55E00", rep("#009E73",2), rep("#0072B2",4)))+
  scale_fill_manual("Species_1",values=c(rep("#D55E00",2),"#E69F00","#D55E00", rep("#009E73",2), rep("#0072B2",4)))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("H)",italic(' P. integrifolia'))))

#SOLY
load("effect_size_species/soly_effect_size.RData")
p9<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0,0.3,0,1), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",1),"#E69F00",rep("#D55E00",2), rep("#009E73",2), rep("#0072B2",4)))+scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("I)",italic(' S. lycopersicum'))))

#SOME
load("effect_size_species/some_effect_size.RData")

p10<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+ geom_point(size=1.5,alpha=c(1,1,1,1,1,1,1,1,1,1),show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(size=0.6,alpha=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c("#E69F00",rep("#D55E00",3), rep("#009E73",2), rep("#0072B2",4)))+
  scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena'))))

sp_legend <- readRDS("Data/sp_legend.RData")
p11<- ggplot(sp_legend, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),plot.margin = unit(c(0,0,0,0.3), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00","#009E73","#E69F00","#0072B2"))+ scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2","#0072B2"))+
  xlab("") + ylab("Hedges' g") +geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena')))) 
 #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
grid.newpage()

g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(p11)

 grid.draw(arrangeGrob(cbind(ggplotGrob(p1+theme(legend.position="none")),ggplotGrob(pp2+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p3+theme(legend.position="none")),ggplotGrob(p4+theme(legend.position="none")),size="last"),cbind(ggplotGrob(p5+theme(legend.position="none")),ggplotGrob(p6+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p7+theme(legend.position="none")),ggplotGrob(p8+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p9+theme(legend.position="none")),ggplotGrob(p10+theme(legend.position="none")),size="last"),mylegend,nrow=6))
#mylegend
```

```{r, echo=FALSE, message=FALSE,warning=FALSE,cache=FALSE,fig.height=8,fig.width=7,fig.cap="A"}
library(effsize)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)
library(tidyverse)

load("effect_size_species/some_effect_size_family.RData")

pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,aes(color=factor(Family))) + theme(legend.title = element_blank(),legend.direction="horizontal")+
  geom_linerange(size=0.6,linetype=1, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("effect_size_species/soly_effect_size_family.RData")

pp2<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("effect_size_species/sial_effect_size_family.RData")

p3<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("effect_size_species/pein_effect_size_family.RData")

p4<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("effect_size_species/ippu_effect_size_family.RData")

p5<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("effect_size_species/ipaq_effect_size_family.RData")

p6<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("effect_size_species/ersa_effect_size_family.RData")

p7<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("effect_size_species/caan_effect_size_family.RData")

p8<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("effect_size_species/brra_effect_size_family.RData")

p9<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("effect_size_species/brol_effect_size_family.RData")

p10<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

 #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
grid.newpage()
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}
leg_family=readRDS("Data/leg_family.RData")
p11<- ggplot(leg_family, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),axis.text.y = element_blank())+ geom_point(size=2,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00","#009E73","#E69F00","#0072B2"))
 #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
mylegend<-g_legend(p11)

 grid.draw(arrangeGrob(cbind(ggplotGrob(pp1+theme(legend.position="none")),ggplotGrob(pp2+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p3+theme(legend.position="none")),ggplotGrob(p4+theme(legend.position="none")),size="last"),cbind(ggplotGrob(p5+theme(legend.position="none")),ggplotGrob(p6+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p7+theme(legend.position="none")),ggplotGrob(p8+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p9+theme(legend.position="none")),ggplotGrob(p10+theme(legend.position="none")), size="last"),mylegend,nrow=6))

```{r, echo=FALSE, message=FALSE,warning=FALSE,cache=FALSE,fig.cap="Phylogenetic signal of the average heterospecific pollen effect size per species"}
library(ape)
library(phylosignal)
library(adephylo)
library(phylobase)
library(phylosignal)
library(caret)
library(ggplot2)
library(seqHMM)
library(dplyr)
library(reshape2)
pollen_tree=read.tree("Data/pollen_tree_no_outgroup.nwk")
effect_size_all <- readRDS( "Data/effect_size_all.RData")
#Now rename species
rownames(effect_size_all) <- c("Solanum_melongena","Solanum_lycopersicum","Petunia_integrifolia", "Capsicum_annuum","Ipomoea_purpurea","Ipomoea_aquatica","Sinapis_alba","Eruca_vesicaria","Brassica_rapa", "Brassica_oleracea")
hp_mean_sp=effect_size_all[,-c(1,3,4)]
p4d <- phylo4d(pollen_tree, hp_mean_sp)
barplot.phylo4d(p4d, center = TRUE , scale = FALSE,trait.labels="Hp effect",bar.col = c(rep("#0072B2",4), rep("#009E73",2), rep("#D55E00",4)))
```

```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE, fig.height=3,fig.width=5,fig.cap="a"}
load("Data/family_cor.RData")
library(ggpubr)
library(ggplot2)
library(gridExtra)
library(grid)

p1 <- ggscatter(sola, x = "Cohen_d", y = "style_length", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Hedges' g", ylab = "Style length (mm)", main="A) Solanaceae")

p2<- ggscatter(a, x = "Cohen_d", y = "style_length", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Hedges' g", ylab = "Style length (mm)", main="A) All families")
grid.arrange(p1, p2, nrow = 1, ncol=2)

@@

```{r write_citations, cache=FALSE, include=FALSE}
write.bibtex(file="knitcitations.bib")
```

<div id = "refs"></div>
\newpage

# APPENDIX

1.

**Table S1**. Perecentage of seeds produced per ovule for the ten species used in the experiment. The treatments presented are hand cross-pollination, hand self-pollination, natural selfing and apomixis (emasculated flowers).
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
load("table_treatments.RData")
Species <- c("Brassica oleracea", "Brassica rapa", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
Cross <- cross
Self <- self
Natural_selfing <- nat_self
Apomixis <- apo
table<- data.frame(Species, Cross, Self, Natural_selfing,Apomixis)
kable(table, format="markdown")
```

2.

**Figure S1**. Pollen ratios separated by family A) Brassicaceae, B) Solanaceae, C) Convolvulaceae. Pollen was counted for crosses with species of the other two families (N=3). To prepare these ratios all the pollen grains on the stigma were counted.

```{r, echo=FALSE, message=FALSE,fig.height=10,fig.width=5, warning=FALSE,fig.cap="Pollen ratios separated by family A) Brassicaceae, B) Solanaceae, C) Convolvulaceae. Pollen was counted for crosses with species of the other two families (N=3). To prepare these ratios all the pollen grains on the stigma were counted.", cache=FALSE}
load("pollen_ratio.RData")
library(ggpubr)
library(ggplot2)
library(gridExtra)
library(grid)

>>>>

---
title: ''
output:
  pdf_document: default
  html_document: default
header-includes:
    - \usepackage{setspace}
    - \doublespacing
    - \usepackage{lineno}
    - \linenumbers
bibliography:
- references.bib
- knitcitations.bib
---
```{r knitcitations, echo=FALSE, cache = FALSE}
library(knitcitations)
cleanbib()   
cite_options(citation_format = "pandoc")
```

@@

@@

@@

@@

<div id = "refs"></div>
